Estimating initial state and quark-gluon plasma medium properties\\ using a hydrodynamic model with nucleon substructure\\calibrated to p-Pb and Pb-Pb collisions at $\sqrts=5.02$~TeV

### 2018-03-24 paper/trento-partons.tex
merge in paper and talk

\subsection{Bayesian calibration}

@@

>>>>

\subsection{Bayesian calibration}
\fig{observables_design}{Caption}

@@

\begin{figure}
  \begin{tikzpicture}
    \foreach \x in {0pt, 10pt, 20pt}{\draw (\x, 0) ellipse (5pt and 20pt);}
    \foreach \x in {0pt, 10pt, 20pt, 30pt}{\draw (\x+100pt, 0) ellipse (5pt and 20pt);}
  \end{tikzpicture}
  \caption{\label{fig:collision} This is the figure caption}
\end{figure}
Consider a relativistic collision between a columnated stack of $n_1$ projectile nucleons and $n_2$ target nucleons as depicted in Fig.~\ref{fig:collision}.
Moreover, assume that each nucleon has mass $m$ and moves with velocity $\pm u$ along the beam axis $\hat{z}$.
The four-momentum of each colliding nucleon stack is given by
\begin{align}
  p_1 &= n_1 \gamma m\, (1, 0, 0, u),\\
  p_2 &= n_2 \gamma m\, (1, 0, 0, -u),
\end{align}
where $\gamma = 1/\sqrt{1 - u^2}$ is the usual Lorentz factor.

At relativistic energies $\gamma \gg 1$, each stack of nucleons is significantly Lorentz contracted in the lab frame and appears compressed along its direction of motion.
The nucleons are thus observed to penetrate and pass through each other in the lab frame in time
\begin{equation}
  \Delta t = L / \sqrt{\gamma^2 - 1}, 
\end{equation}
where $L\sim1$--10~fm is the length of the columnated stack of nucleons in its local rest frame.

Collisions at top RHIC and LHC energies have interpenetration times \mbox{$\Delta t < .1$~fm/$c$} and hence transpire before meaningful dynamics develop in the transverse plane.
For this reason, it is convenient to say that initial energy deposition occurs instantaneously at time $\Delta t = 0^+$, the moment the two nuclei collide.
The initial energy (or entropy) deposited into the transverse plane is then modeled in terms of two beam-integrated nuclear thickness functions
\begin{equation}
  T_{A,B}(x, y) = \int dz \rho(x, y, z),
\end{equation}
where $\rho$ is the density profile of the nucleus in its local rest frame.
